### 2023-09-11 README.Rmd
fixing suppl link

- Paper [PDF](documents/paper/paper.pdf)
- Supplementary Materials [PDF](documents/supplementary/supplementary.pdf)

>>>>

| **Document** | **Rendered** | **Source** |
|---|---|---|
| Paper | [pdf](documents/paper/paper.pdf) | [rmd](documents/paper/paper.Rmd) |
| Supplementary Materials | [pdf](documents/paper/supplementary.pdf) | [rmd](documents/paper/supplementary.Rmd) |
